\documentclass{article}
\usepackage{amsmath, amssymb, fullpage, listings}
\begin{document}
\vspace*{0.1cm}

\section*{\S 3.1}
\begin{enumerate}
\item[3.1.3.1]
  \begin{enumerate}
  \item
    %% 0, 1.5, -.66, 1.25, -.8, ...
    \begin{description}
    \item[sup]
      1.5
    \item[inf]
      -1
    \item[limsup]
      1
    \item[liminf]
      -1
    \item[limits]
      1, -1
    \end{description}
  \item
    \begin{description}
    \item[sup]
      $\frac{3}{2}$
    \item[inf]
      0
    \item[limsup]
      1
    \item[liminf]
      1
    \item[limits]
      1
    \end{description}
  \item
    \begin{description}
    \item[sup]
      2
    \item[inf]
      -3
    \item[limsup]
      1
    \item[liminf]
      -3
    \item[limits]
      -3, 1
    \end{description}
  \end{enumerate}
\item[]
\item[3.1.3.2]
  No, the sequences don't necessarily converge. 
  Example: $\{y_n\} = .9, .99, .999, \ldots$ 
  $\{z_n\} = -.9, -.99, -.999, \ldots$ 

  Bounding the sequences doesn't help. My example sequences are bounded. 
  Yeah, I can't even think of an example where $\{y_n\}$ and $\{z_n\}$ are
  \emph{unbounded} but the sequence $x_n = y_n + z_n$ \emph{is} bounded.
  %% Harris help ^
\item[]
\item[3.1.3.3]
  $y_n$ is an upper bound for $E$ because it is the limit of upper bounds. 
  $y_n$ is the least upper bound because it is the limit of elements $x_n$
        of $E$.
\item[]
\item[3.1.3.4]
  The union takes elements from both sets, so the suprenam can only increase. 
  The intersection only removes elements. If $sup(B) > sup(A)$, then we
  know that $sup(B) \not\in A$ and therefore $sup(B) \not\in A \cap B$.
\item[]
\item[3.1.3.5]
  %% I don't understand this one. 
  %% Doesn't this inequality fail for:
  %%  x_n = 1, 1, 1, \ldots
  %%  y_n = -10, -10, \ldots
  %% Because the limsup of the shuffled sequence is 1, 
  %% which is less than the sum of the limsups of x_n \& y_n, which are
  %% 1 and -10, respectively. 

  TODO prove first part.

  Equality does not hold for $x_n = 1, 1, 1, \ldots$
  and $y_n = 1, 1, 1, \ldots$. 
  Each has a limsup of 1, and so does their shuffled sequence. 
  Hence $limsup\{ x_n + y_n \} < limsup\{ x_n \} + limsup\{ y_n \} \rightarrow
  1 < 1 + 1$.

\item[]
\item[3.1.3.6]
  Yes. 
  %% Every elements of sub-sub-sequence $\{x^{\prime\prime}_n\}$
  %% is an element of subsequence $\{x^{\prime}_n}$; in turn, every element
  %% of $\{x^\prime_n\}$ is an element of $\{x_n\}$. Thus 
  Members of the subsubsequence are members of the parent sequence,
  so one can define a subsequence selection function to extract it from
  the parent sequence. 
 \item[]
\item[3.1.3.7]
  Create two infinite matrices:
\item[]
  \begin{tabular}{ c c c c c}
   0 & 1 & 2 & 3 & \ldots \\
   0 & 1 & 2 & 3 & \ldots \\
   0 & 1 & 2 & 3 & \ldots \\
   0 & 1 & 2 & 3 & \ldots \\
   \vdots & \vdots & \vdots & \\
  \end{tabular}
  \begin{tabular}{ c c c c}
  -1 & -2 & -3 & \ldots \\
  -1 & -2 & -3 & \ldots \\
  -1 & -2 & -3 & \ldots \\
  -1 & -2 & -3 & \ldots \\
   \vdots & \vdots & \vdots & \\
  \end{tabular}

  Diagonialize each and shuffle those resulting sequences. 
  Now we have a sequence in which each integer appears an infinite
  number of times. 
\item[]
\item[3.1.3.8]
  $\Rightarrow$: Limits of subsequences are limits of the sequence. 

  $\Leftarrow$: Choose the sequence itself as a subsequence.
    (Or delete a finite number of elements.)
\item[]
\item[3.1.3.9]
  Yes. Create another matrix and diagonalize it. The liminf is zero.
\item[]
  \begin{tabular}{c c c c}
   1 & $\frac{1}{2}$ & $\frac{1}{3}$ & \ldots \\
   1 & $\frac{1}{2}$ & $\frac{1}{3}$ & \ldots \\
   1 & $\frac{1}{2}$ & $\frac{1}{3}$ & \ldots \\
   1 & $\frac{1}{2}$ & $\frac{1}{3}$ & \ldots \\
   \vdots & \vdots & \vdots & \\
  \end{tabular} 
\item[]
\item[3.1.3.10]
  Limits of subsequences are limits of sequences. If an infinite
  number of terms in a subsequence approach a limit point, then it 
  follows that an infinite number of terms in the sequence approach the
  same limit. They're the same terms!

  Sequences have no limits that do not belong to their subsequences. 
  Assume, for contradiction, that the sequence $x_n = y_n + z_n$ has 
  a limit point $l$ such that neither an infinite number of terms 
  of $y_n$ nor an infinite number of terms of $z_n$ approach $l$. 
  In other words, no more than a finite number of $y\in y_n$ and 
  $z \in z_n$ approximate the limit. Then only finitely many $x\in x_n$
  could possibly approach $l$, a contradiction.

  Shuffling doesn't matter. The order in which subsequence terms appear
  in the final sequence has no bearing on whether an infinite number of 
  sequence terms fall within some epsilon of a limit.
\item[]
\item[3.1.3.11]
  Rows and columns appear as subsequences, so their limits appear in the
  sequence. A definition for the row subsequence selection function, 
  defined in terms of the row number, $r$, where the top row of the matrix
  is row $r=1$:

  \[f_r = 1\ \text{when}\ r=0\]

    \[f_r(i) = f_{r-1}(1) + r - 1\ \text{when}\ i=1\]

    \[f_r(i) = f_r(i-1) + i + r - 1\ \text{else}\ \]

  %% What does "all limit points" mean? All row/col limits or all limits 
  %% of matrix entries?
  Yes, one necessarily gets all limit points in this way. 
  All the matrix terms appear in the sequence. How could you not?

  
  %% Here are OCaml implementations of the row subsequence selection 
  %% function. The function assumes a predefined stream type. 
  %% I'm not sure how to express this mathematically.
  %% \begin{lstlisting}
  %% let row_subsequence row_num = 
  %%   let offset = ref 1 in
  %%   let rec row prev_index = 
  %%     incr(offset);
  %%     let next_index = prev_index + !offset in
  %%     Cons(next_index, fun () -> row next_index)
  %%   in Cons(row_num, fun () -> row row_num)
  %% \end{lstlisting}
\item[]
\item[3.1.3.12]
  Reflexivity \& symmetry are easy. Any sequence differs from 
  itself in finitely many (i.e. zero) terms, and if $x$ differs from 
  $y$ in $n$ terms then obviously $y$ and $x$ will be identical after $n$
  terms. 
  For transitivity, say $x$ and $y$ differ by $n$ terms and $y$ and $z$
  differ by $m$ terms. Then $x$ and $z$ differ by $max(n,m)$ terms. 
  If $z$ is  the same sequence as $y$ after a finite number of steps
  then it's obviously also identical to $x$ after finitely many steps. 

  Equivalent sequences have the same limit points because they have
  the same behavior at infinity. They are exactly the same for 
  an infinite number of terms. 
\end{enumerate}

\newpage
\vspace*{0.1cm}
\section*{\S 3.2}
\begin{enumerate}
\item[3.2.3.1]
  Let $A=(a, b)$ be the open set and let 
  $x_1, x_2, \ldots x_n$ be the points removed from $A$,
  arranged in ascending order. We know that $a<x_1$ and 
  $x_n < b$, so we can define the new set $A^\prime$ obtained
  by deleting all the points as the union of open intervals
  $(a, x_1) \cup (x_2, x_3) \cup \ldots \cup (x_n, b)$. 
  The union of open intervals is open, thus $A^\prime$ is open.

  The same holds if a countable number of points are removed. 
  Let $A=\mathbb{R}$ and remove $\mathbb{N}$ from $A$. 
  Now $A^\prime$ is the union $(-\infty, 1) \cup (1, 2) \cup (2, 3) \ldots$, 
  which is an open set. 
\item[]
\item[3.2.3.2]
\item[]
\item[3.2.3.3]
\item[]
\item[3.2.3.4]
  This seems like it follows trivially from the definitions. 
\item[]
\item[3.2.3.5]
  If $A$ is a closed set, $x$ is a point in $A$, and $B = A - \{ x \}$, 
  then $B$ is closed when $x$ is not a limit point of $A$. Why?
  Because $B$ will then contain all its limit points, just like $A$
  did, making it a closed set. 
\item[]
\item[3.2.3.6]
\item[]
\item[3.2.3.7]
\item[]
\item[3.2.3.8]
\item[]
\item[3.2.3.9]
\item[]
\item[3.2.3.10]
\item[]
\item[3.2.3.11]
\item[]
\item[3.2.3.12]
\item[]
\item[3.2.3.13]
\item[]
\item[3.2.3.14]
  The empty set and the universe of all sets are both open and closed 
  by definition.
\item[]
\item[3.2.3.15]
  Let $\bigcup \mathcal{A}$ be a union of open intervals. 
  Replace every pair of intersecting intervals $(a, b), (c, d) \in \mathcal{A}$
  by the interval $(min(a, c), max(b, d))$. 
  What's left is to prove that this is really equivalent. % TODO
\item[]
\item[3.2.3.16]
  Let $\bigcup \mathcal{A}$ and $\bigcup \mathcal{B}$ be two ways of
  describing the same open set. Let $(a_1, a_2)$ and $(b_1, b_2)$
  be the intervals in 
  $\mathcal{A}$ and $\mathcal{B}$, respectively,
  with the smallest first element. 
  Now $a_1 \le b_1$, otherwise $(b_1, b_2)$ would include the limit $a_1$.
  Likewise $b_1 \le a_1$ because 
  otherwise $(a_1, a_2)$ would include $b_1$. Hence $a_1 = b_1$. 
  A similar argument holds for $a_2$ and $b_2$, so the intervals 
  must be the same. Removing these smallest intervals and applying the
  same argument inductively, we see that $\mathcal{A}$ must be the 
  same set as $\mathcal{B}$.
\item[]
\end{enumerate}
\end{document}
